---
title: "Regression Project"
author: "Brandon Harden, Julie Fisher, Karelys Osuana, Mingjian Shi"
date: "April 23, 2017"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(corrplot)
comm_prop <- tbl_df(read_csv("comm_prop.csv"))
```

# Examination of dataset

For our initial examination of the data, we looked at the number of rows and columns, the variable names, a sample of the first five rows, and some basic statistics (min, max, mean, median, and IQR info).


```{r examination}
dim(comm_prop)
names(comm_prop)
head(comm_prop)
summary(comm_prop)
```
## Visualize relationships

Next we created visualizations to see how the variables relate to our variable of interest RentRate.

```{r}
df.full <- lm(RentRate ~ ., data = comm_prop)
summary(df.full)
cor(comm_prop)
corrplot(cor(comm_prop), method="ellipse")
```
## Initial evaluation

From the review of these results, it appears that VacRate, SqFt, and Taxes are all minimally significant. So we removed them and reran the calculations.
```{r}
dfLessMin <- lm(RentRate ~ Age + OperExp + W2MiDT, data = comm_prop)
summary(dfLessMin)
```
## Review evaluation

The R^2 and adjusted R^2 showed significant reduction, so we reviewed the variables for multicollinearity and found that SqFt and taxes are highly corelated (over .999). It appears taxes are based mainly on square footage, with possibly some consideration for location. Location is also already addressed by the M2MiDT variable. As such, our group decided to remove Taxes as it appears to be corelated to both SqFt and M2MiDT.

We added SqFt back in and reran the calculations. These calculations show results almost as good as those of all the variables, but a factor of potential overfitting.
```{r}
df_model <- lm(RentRate ~ Age + OperExp + W2MiDT + SqFt, data = comm_prop)
summary(df_model)
```
## Data Clean
At this point we converted W2MiDT to a factor: 0 to 'No' and 1 'Yes'

```{r createfactor}
comm_prop$W2MiDT <- factor(comm_prop$W2MiDT, labels = c("No", 'Yes'))
show(comm_prop$W2MiDT)
```
## Visual Representation

Next we created visual representations to get a feel for the distribution of the data.

```{r}
hist(comm_prop$RentRate, xlab = "Rent Rate", main = paste("Rent Rate (In Thousands)"), col = "indianred")

hist(comm_prop$Age, xlab = "Age", main = paste("Age"), col = "indianred")

hist(comm_prop$OperExp, xlab = "Total Monthly Operating Expenses", main = paste("Total Monthly Operating Expenses (In Thousands)"), col = "indianred")

hist(comm_prop$VacRate, xlab = "Vacancy Rate", main = paste("Vacancy Rate"), col = "indianred")

hist(comm_prop$SqFt, xlab = "Total Square Footage", main = paste("Total Square Footage"), col = "indianred") 
  
hist(comm_prop$Taxes, xlab = "Taxes", main = paste("Total Monthly Tax Expense (In Thousands)"), col = "indianred")

ggplot(comm_prop$W2MiDT) +
  stat_histogram() +
  labs(x = "Region", y = "Birth Rate")

hist(comm_prop$W2MiDT, xlab = "Building Located Within 2 Miles of Downtown", main = paste("Location"), col = "indianred")

pairs(comm_prop[,1:6], pch = 16)
```
## Examine residuals, normality, variance, and any other multicollinearity
```{r}
full.df <- fortify(df_model)
ggplot(full.df, aes(x=.fitted, y=.resid)) +
  geom_point() +
  geom_hline(yintercept=0, linetype=2) +
  labs(x="Fitted Values", y="Residuals")

qqPlot(df_model$residuals, pch=16)
shapiro.test(df_model$residuals)
pairs(comm_prop[-c(4,6)], pch=16)

ncvTest(df_model)

vif(df_model)
```
These results seem to fall with acceptable results. And so we moved on to quality of fit
```{r}
ggplot(full.df, aes(x=.fitted, y=RentRate)) +
  geom_point(size=2) +
  geom_smooth(method="lm", color="red", lwd=1.5) +
  labs(x="Rent Predicted", y="Rent Actual")
```
## What to charge

Of course now we have to figure out what to actually charge.
```{r}
new_RentRate <- data.frame(Age=9, OperExp=13, SqFt=40, Taxes=540, W2MiDT='No')
predict(df_model, newdata=new_RentRate, interval="predict")
```
