---
title: "Regression Project"
author: "Brandon Harden, Julie Fisher, Karelys Osuana, Mingjian Shi"
date: "April 23, 2017"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(car)
library(corrplot)
comm_prop <- tbl_df(read_csv("comm_prop.csv"))
```

# Examination of dataset

For our initial examination of the data, we looked at the number of rows and columns, the variable names, a sample of the first five rows, and some basic statistics (min, max, mean, median, and IQR info).


```{r examination}
dim(comm_prop)
names(comm_prop)
head(comm_prop)
summary(comm_prop)
```

## Data Clean

This review showed that the variable 'W2MiDT' is a factor. We converted the 0 and 1 results to 'Yes' and 'No'.

```{r createfactor}
comm_prop$W2MiDT <- factor(comm_prop$W2MiDT, labels = c("No", 'Yes'))
show(comm_prop$W2MiDT)
```

## Visual Representation

Next we created visual representations to get a feel for the distribution of the data.

```{r}
hist(comm_prop$RentRate, xlab = "Rent Rate", main = paste("Rent Rate (In Thousands)"), col = "indianred")

hist(comm_prop$Age, xlab = "Age", main = paste("Age"), col = "indianred")

hist(comm_prop$OperExp, xlab = "Total Monthly Operating Expenses", main = paste("Total Monthly Operating Expenses (In Thousands)"), col = "indianred")

hist(comm_prop$VacRate, xlab = "Vacancy Rate", main = paste("Vacancy Rate"), col = "indianred")

hist(comm_prop$SqFt, xlab = "Total Square Footage", main = paste("Total Square Footage"), col = "indianred") 
  
hist(comm_prop$Taxes, xlab = "Taxes", main = paste("Total Monthly Tax Expense (In Thousands)"), col = "indianred")

ggplot(comm_prop$W2MiDT) +
  stat_boxplot(geom = "errorbar", width = 0.5) +
  geom_boxplot() +
  coord_flip() + # Makes regions names easier to read
  labs(x = "Region", y = "Birth Rate")

hist(comm_prop$W2MiDT, xlab = "Building Located Within 2 Miles of Downtown", main = paste("Location"), col = "indianred")

pairs(comm_prop[,1:6], pch = 16)
```
# Correlations for continuous variables
```{r}
cor(comm_prop[,1:6])
```

